\documentclass[10pt]{article}
\usepackage{palatino}
\usepackage[utf8]{inputenc}   % pro unicode UTF-8
\usepackage[IL2]{fontenc}
\usepackage{a4wide}
\usepackage{amsmath,amsfonts,amssymb,graphicx}
\usepackage{wrapfig}
\usepackage{hyperref}
\usepackage{fontawesome}


\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    urlcolor=blue,
    citecolor=blue
}


\begin{document}

\begin{center}
\textbf{\LARGE Ing. Josef Štěpáník} \\
\end{center}

\textbf{Personal information} 

\begin{tabbing}
    \hspace{6cm}\= \kill
    Birth date: \> 5. 4. 1988 \\
    Permanent address: \> Kejnice 6, 341 01 Horažďovice \\
    Current address: \> Žitná 1731/44, 621 00 Brno-Řečkovice \\
    Phone: \> \faPhone \ +420 724 160 236 \\
    Email: \> \faEnvelope \ \href{mailto:stepjo.hd@gmail.com}{stepjo.hd@gmail.com} \\
    LinkedIn: \>  \faLinkedin \ \href{https://www.linkedin.com/in/josef-štěpáník-30106174/}{Josef Štěpáník} \\
    GitHub: \>  \faGithub \ \href{https://github.com/JosefStepanik}{Josef Stepanik} \\
    Instagram: \>  \faInstagram \ \href{https://www.instagram.com/josef_stepanik/}{josef\_stepanik}
\end{tabbing}

\noindent\hrulefill
\vskip 0,4cm

\textbf{Professional summary}
\vskip 0,3cm

\indent I would describe myself as a practical technician and developer with experience in designing and implementing custom equipment and measurement technology.
Capable of independently or collaboratively solving technical problems, ranging from hardware design to basic programming and automation. \\
\indent My professional traits include strong communication skills, a willingness to learn new things, and a conflict-free approach. I am also motivated by a competitive and sporting spirit.
\vskip 0,3cm

\noindent\hrulefill
\vskip 0,4cm

\textbf{Previous employment}

\begin{itemize}
\item \textbf{IQS nano s.r.o.} [2022 - present], position: technician, programmer. Development and production of custom equipment for research and manufacturing in the field of nanotechnologies.
\item \textbf{Activair s.r.o.} [2017 - 2022], position: electrical engineer. Design and development of equipment in the field of vacuum technology, including manipulators and distribution systems.
\item \textbf{CEITEC VUT Brno} [2019 - 2021], position: technician, laboratory manager, research group Advanced Instrumentation and Methods for Materials Characterization - Josef Kaiser. 
Development of measurement technology for the study and testing of thin films of materials.
\item \textbf{Rohde \& Schwarz} [2014 - 2017], position: product engineer. Support for development and production of measurement equipment for telecommunications and broadcasting.
\end{itemize}

\noindent\hrulefill
\vskip 0,4cm

\textbf{Education}

\begin{itemize}
    \item [\faGraduationCap]\textbf{Czech technical university Prague, Faculty of Electrical Engineering}
    \begin{itemize}
        \item study program: Electronics and communications, study plan: Media and signal processing - Master's degree (Ing.) [2011 - 2014]
        \item Master's thesis: Image sharpening with Curvelet transform.
        \item study program: Electrical engineering and computer science, study plan: Electronics - Bachelor's degree. [2007 - 2011]
    \end{itemize}
    \item[\faGraduationCap] \textbf{Grammar school Jaroslava Vrchlického, Klatovy} [2004 - 2007]
\end{itemize}

\noindent\hrulefill
\vskip 0,4cm

\textbf{Skills}

\begin{itemize}
    \item \textbf{Professional skills:} 
    \begin{itemize}
        \item Matlab, Microwave Office (RF/Microwave circiut desing), CST Microwave Studio (3D EM Simulations).
        \item developing utilities in Visual Studio Code with Python, PyQt, Angular , Wiring (C++), HTML5 languages. Using version control system GIT.
        \item printed circuit board design in Autodesk Eagle.
        \item cooperation with mechanical designer in Autodesk Fusion360.
        \item process schematics and wires in SW Proficad.
    \end{itemize}
    \item \textbf{Měřící technika:} obsluha a integrace běžných laboratorních měřících přístrojů (zdroj, osciloskop, spektrální analyzátor atd).
    \item \textbf{Automation:} design automation systems for PLC in special devices, making working utilites according to IEC 61131-3 standard, communication
    with Modbus, EtherCat, RS485/RS232, OPC UA, etc. Creating of GUI.
    \item \textbf{3D printing:} experience wiht Funmat HT (filaments Peek, Pekk, etc), Markforged MarkTwo (nylon + fiber of carbon, kevlar, fiberglass), Formlabs Form 3 (LFS), DeltiQ (standard filaments). 
    Preparing of printing files in different SW.
    \item \textbf{PC others:} MS Office, \LaTeX, Affinity Photo, Adobe Photoshop, DaVinci Resolve.
    \item \textbf{Languages:} english - intermediate, german – elementary.
    \item \textbf{Driving licence:} category B.
\end{itemize}

\noindent\hrulefill
\vskip 0,4cm

\end{document}